---
title: "EDA_LA2"
author: "Sanjay_Amith"
date: '2022-07-03'
output:
  html_document: default
  word_document: default
---
## Loading Data
```{r}
netflix_data=read.csv("/home/sanjana/Downloads/NetflixOriginals.csv",header=TRUE,sep=",")
```
```{r}
head(netflix_data,n=20)
```
# # EXPLORING DATA
# # Creating a Scatter Plot
```{r}
plot(netflix_data$IMDB.Score, netflix_data$runtime)
```
 With ggplot2, you can get a similar result using the ggplot() function 
```{r}
library(ggplot2)
ggplot(netflix_data, aes(x = IMDB.Score, y =Runtime )) +
geom_point()
```
 The first part, ggplot(), tells it to create a plot object, and the second part,


# # Creating a Line Graph

```{r}
plot(pressure$temperature, pressure$pressure, type = "l")
```
```{r}
plot(netflix_data$IMDB.Score, netflix_data$runtime, type = "l")
points(netflix_data$IMDB.Score, netflix_data$runtime)
```

With ggplot2, you can get a similar result using geom_line()
```{r}
library(ggplot2)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_line()
```
```{r}
library(ggplot2)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_line()+geom_point()
  
```
```{r}

```



# # Creating a Bar Graph
```{r}


```
With ggplot2, you can get a similar result using geom_col()
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_col()
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score)) +
geom_bar()
```
```{r}

```
# # Creating a Histogram
```{r}
hist(netflix_data$IMDB.Score, breaks = 10)
```
 With wider bins
```{r}
ggplot(netflix_data, aes(x = IMDB.Score)) +
geom_histogram(binwidth = 4)
```
# # Creating a Box Plot

With the ggplot2 package, you can get a similar result (Figure 2-11, left) with
geom_boxplot():
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_boxplot()
```

```{r}
curve(x^3 - 5*x, from = -4, to = 4)
```
With ggplot2, you can get a similar result (Figure 2-13), by using stat_func
tion(geom = "line")
Using add = TRUE will add a
curve to the previously created plot:
```{r}
myfun <- function(xvar) {
1 / (1 + exp(-xvar + 10))
}
curve(myfun(x), from = 0, to = 20)
curve(1 - myfun(x), add = TRUE, col = "red")
```
```{r}

# This sets the x range from 0 to 20
ggplot(data.frame(x = c(0, 20)), aes(x = x)) +
stat_function(fun = myfun, geom = "line")
```
# # Making a Basic Bar Graph
You have a data frame where one column represents the x position of each bar, and
another column represents the vertical (y) height of each bar.
Use ggplot() with geom_col()
```{r}
library(gcookbook)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_col()

```

```{r}
head(netflix_data)
```
```{r}
ggplot(netflix_data, aes(x = Runtime, y = IMDB.Score)) +
geom_col()
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_col()
```
# Convert Time to a discrete (categorical) variable with factor()
```{r}
ggplot(netflix_data, aes(x = factor(Runtime), y = IMDB.Score)) +
geom_col()
```
we use a light blue fill and a black outline
```{r}
ggplot(netflix_data, aes(x = Runtime, y = IMDB.Score)) +
geom_col(fill = "lightblue", colour = "black")
```
# # Grouping Bars Together
```{r}
library(gcookbook)
ggplot(netflix_data, aes(x = IMDB.Score, y = IMDB.Score, fill = Runtime))
```
# #Making a Bar Graph of Counts
```{r}
ggplot(netflix_data, aes(x = Runtime)) +
geom_bar()
```
# #Using Colors in a Bar Graph
You want to use different colors for the bars in your graph
```{r}
library(gcookbook)
library(dplyr)
upc<- netflix_data  %>%
arrange(desc(IMDB.Score)) %>%
slice(1:10)
```
```{r}
ggplot(upc, aes(x = Genre, y = IMDB.Score, fill = Language)) +
geom_col()
```
```{r}

library(dplyr)
ggplot(upc, aes(x = reorder(Genre, IMDB.Score), y = IMDB.Score, fill = Language)) +
geom_col(colour = "black") 
  

```
# #
```{r}
climate_sub <- netflix_data %>%
filter(Language == "English" & Runtime >= 80) %>%
mutate(pos = IMDB.Score >= 0)
```
```{r}
ggplot(climate_sub, aes(x = Genre, y = IMDB.Score, fill = pos)) +
geom_col(position = "identity")
```
```{r}
ggplot(climate_sub, aes(x = Genre, y = IMDB.Score, fill = pos)) +
geom_col(position = "identity", colour = "black", size = 0.25) +
scale_fill_manual(values = c("#CCEEFF", "#FFDDDD"), guide = FALSE)
```
# # Adjusting Bar Width and Spacing
```{r}
library(gcookbook)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_col()
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_col(width =0.5)
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, fill = Language)) +
geom_col(width = 0.5, position = "dodge")
```
# # Making a Stacked Bar Graph
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, fill = Language)) +
geom_col()
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, fill = Language)) +
geom_col()+guides(fill = guide_legend(reverse = TRUE))
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, fill = Language))+geom_col(colour = "black") +
scale_fill_brewer(palette = "Pastel1")
```
# # Adding Labels to a Bar Graph
```{r}
library(gcookbook)
ggplot(netflix_data, aes(x = interaction( Language,IMDB.Score), y = IMDB.Score)) +
geom_col() +
geom_text(aes(label = IMDB.Score), vjust = 1.5, colour = "white")
```
```{r}
ggplot(netflix_data, aes(x = factor(Runtime))) +
geom_bar() +
geom_text(aes(label = ..count..), stat = "count", vjust = 1.5,
colour = "white")
```
```{r}
ce <- netflix_data %>%
arrange(Language, rev(Title))
```
```{r}

```
# # Making a Cleveland Dot Plot
```{r}
library(gcookbook) 
tophit <- netflix_data[1:25, ]
ggplot(tophit, aes(x = IMDB.Score, y = Genre)) +
geom_point()
```
```{r}
ggplot(tophit, aes(x = IMDB.Score, y = reorder(Title, IMDB.Score))) +
geom_point(size = 3) +
theme_bw() +
theme(
panel.grid.major.x = element_blank(),
panel.grid.minor.x = element_blank(),
panel.grid.major.y = element_line(colour = "grey60", linetype = "dashed")
)
```
# #Making a Basic Scatter Plot
```{r}
library(gcookbook) 
library(dplyr)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_point()
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_point(shape=21)
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_point(size=1.5)
```
Grouping Points Together Using Shapes or Colors
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, shape = Language, colour = Language)) +
geom_point()
```
```{r}

```
# #Using Different Point Shapes
You want to change the default scatter plot shapes for the data points.
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_point(shape=3 )
```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, shape =Language )) +
geom_point(size = 3) 

```
```{r}
hw <- netflix_data %>%
mutate(weightgroup = ifelse(Runtime < 50, "< 50", ">= 50"))
```
# # Mapping a Continuous Variable to Color or Size
# You want to represent a third continuous variable using color or size.
A basic scatter plot shows the relationship between two continuous variables: one
mapped to the x-axis, and one to the y-axis. When there are more than two continuous
variables, these additional variables must be mapped to other aesthetics, like size
and colour.
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, colour = Runtime)) +
geom_point()
```
```{r}
range(netflix_data$IMDB.Score)
#> [1] 50.5 171.5
size_range <- range(netflix_data$IMDB.Score) / max(netflix_data$IMDB.Score) * 6
size_range
```
you want the diameter of the
points to represent the data values, or if you want the area of the points to represent
the data values.
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, size = IMDB.Score)) +
geom_point() +
scale_size_continuous(range = size_range)
```

```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, size = Runtime)) +
geom_point() +
scale_size_area()
```
When it comes to color, there are actually two aesthetic attributes that can be used:
colour and fill
```{r}
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime, fill = Runtime)) +
geom_point(shape = 21,size=2.5)+
  scale_fill_gradient(
low = "black", high = "white",
breaks = seq(70, 170, by = 20),
guide = guide_legend()
)
```
# #Dealing with Overplotting
You have many points that overlap and obscure each other when plotted
```{r}
diamonds_sp <- ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime))
diamonds_sp +
geom_point()

```
```{r}
diamonds_sp +
geom_point(alpha = .1)
```
```{r}
diamonds_sp +
geom_point(alpha = .01)
```
# #Adding Fitted Regression Model Lines
You want to add lines from a fitted regression model to a scatter plot
```{r}
hw_sp <- ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime))
hw_sp +
geom_point() +
stat_smooth(method = lm)
```
```{r}
hw_sp +
geom_point() +
stat_smooth(method = lm, level = 0.99)
```
```{r}
hw_sp +
geom_point(colour = "grey60") +
stat_smooth(method = lm, se = FALSE, colour = "black")
```
```{r}
hw_sp +
  geom_point(colour = "grey60") +
stat_smooth(method = loess)
```
```{r}
library(MASS)
ggplot(netflix_data, aes(x = IMDB.Score, y = Runtime)) +
geom_point(
position = position_jitter(width = 0.3, height = 0.06),
alpha = 0.4,
shape = 21,
size = 1.5
) +
stat_smooth(method = glm, method.args = list(family = binomial))
```
```{r}
hw_sp +
geom_smooth(method = lm, se = FALSE, fullrange = TRUE)
```
# # Adding Marginal Rugs to a Scatter Plot
You want to add marginal rugs to a scatter plot
```{r}
ggplot(faithful, aes(x = eruptions, y = waiting)) +
geom_point() +
geom_rug()
```
```{r}
ggplot(faithful, aes(x = eruptions, y = waiting)) +
geom_point() +
geom_rug(position = "jitter", size = 0.2)
```





```{r}
netflix_data=read.csv("/home/sanjana/Downloads/NetflixOriginals.csv",header=TRUE,sep=",")
```
```{r}
head(netflix_data,n=20)
```
##Making a Basic Histogram
```{r}
library(ggplot2)

ggplot(netflix_data, aes(x = Runtime)) +
geom_histogram(binwidth = 5,fill = "white", colour = "black")
```
##Making Multiple Histograms from Grouped Data


```{r}
install.packages("MASS")
library(MASS)
library(ggplot2)
ggplot(birthwt, aes(x = bwt)) +
  geom_histogram(fill = "white", colour = "black") +
facet_grid(smoke ~ .)
```

##Making a Density Curve
```{r}
library(ggplot2)
ggplot(netflix_data, aes(x = IMDB.Score)) +
geom_density()

```
```{r}
ggplot(netflix_data, aes(x = IMDB.Score)) +
geom_line(stat = "density") +
expand_limits(y = 0)
```
```{r}
library(ggplot2)
ggplot(netflix_data,aes(x = Runtime)) +
geom_line(stat= "density") +

geom_line(stat= "density", adjust = .25, colour = "red") +

geom_line(stat= "density", adjust = 2, colour = "blue")
```
```{r}
ggplot(netflix_data, aes(x = Runtime)) +
geom_density(fill = "blue", alpha = .2, colour = NA) +
xlim(35, 105) +
geom_line(stat = "density")
```
```{r}
library(MASS)
library(ggplot2)
birthwt_mod <- birthwt
ggplot(birthwt_mod, aes(x = bwt, fill = smoke)) +
geom_histogram(position = "identity", alpha = 0.4)
```
##Combineing both density and histogram
```{r}
ggplot(netflix_data, aes(x = Runtime, y = ..density..)) +
geom_histogram(fill = "cornsilk", colour = "grey60", size = .2) +
geom_density() +
xlim(35, 105)
```
###Making Multiple Density Curves from Grouped Data
```{r}
ggplot(netflix_data, aes(x = Language, fill = as.numeric(IMDB.Score))) +
geom_density(alpha = .3)
```
```{r}
ggplot(birthwt_mod, aes(x = bwt)) +
geom_density() +
facet_grid(smoke ~ .)
```
```{r}
birthwt_mod <- birthwt
ggplot(birthwt_mod, aes(x = bwt, y = ..density..)) +
geom_histogram(binwidth = 200, fill = "cornsilk", colour = "grey60",
size = .2) +
geom_density() +
facet_grid(smoke ~ .)
```
##Making a Frequency Polygon
```{r}
ggplot(netflix_data, aes(x=Runtime)) +
geom_freqpoly()
```

##Making a Basic Box Plot
```{r}
library(MASS)
ggplot(birthwt, aes(x = factor(race), y = bwt)) +
geom_boxplot()
```
##Adding Notches to a Box Plot
```{r}
ggplot(birthwt, aes(x = factor(race), y = bwt)) +
geom_boxplot(notch = TRUE)
```
##Adding Means to a Box Plot
```{r}
ggplot(birthwt, aes(x = factor(race), y = bwt)) +
geom_boxplot() +
stat_summary(fun.y = "mean", geom = "point", shape = 23, size = 3,
fill = "white")
```
##Making a Violin Plot
```{r}
library(gcookbook)
hw_p <- ggplot(heightweight, aes(x = sex, y = heightIn))
hw_p +
geom_violin()
```
```{r}
hw_p +
geom_violin() +
geom_boxplot(width = .1, fill = "black", outlier.colour = NA) +
stat_summary(fun.y = median, geom = "point", fill = "white", shape = 21,
size = 2.5)
```
```{r}
hw_p <- ggplot(heightweight, aes(x = sex, y = heightIn))
hw_p +
geom_violin(adjust = 2)
hw_p +
geom_violin(adjust = 0.5)
```

##Making a Dot Plot
```{r}
library(ggplot2)
library(dplyr)
netflix<- netflix_data %>%
filter(Language == 'English' & Runtime > 50)
# Create a base ggplot object using `c2009`, called `c2009_p` (for c2009 plot)
net <- ggplot(netflix, aes(x = as.numeric(IMDB.Score)))
net +
geom_dotplot()
```
##Making Multiple Dot Plots for Grouped Data
```{r}
library(ggplot2)
ggplot(netflix_data, aes(x =Language, y = as.numeric(IMDB.Score))) +
geom_dotplot(binaxis = "y", binwidth = .5, stackdir = "center"
)
```
```{r}
ggplot(heightweight, aes(x = sex, y = heightIn)) +
geom_boxplot(aes(x = as.numeric(sex) + .2, group = sex), width = .25) +
geom_dotplot(
aes(x = as.numeric(sex) - .2, group = sex),
binaxis = "y",
binwidth = .5,
stackdir = "center"
) +
scale_x_continuous(
breaks = 1:nlevels(heightweight$sex),
labels = levels(heightweight$sex)
)
```
##Making a Density Plot of Two-Dimensional Data
```{r}
library(ggplot2)
faithful_p <- ggplot(netflix_data, aes(x = Runtime, y = IMDB.Score))
faithful_p +
geom_point() +
stat_density2d()
```
```{r}
faithful_p +
stat_density2d(aes(colour = ..level..))
```
